\pdftitle

### 2017-05-16 maxNt.tex
worked on Intro

Recent advances in electrophysiological techniques allow to
record from large population of neurons [\cite]. The recorded neurons
are usually picked out according to an unknown process, and from their
observation we expect to learn something about all other neurons in the
same brain area. That is, they are assumed to be a
\enquote{representative random sample} of the neurons in that area.

@@

Using the pairwise \me\ models many studies strived for answering 
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? add more **

>>>>

Recent advances in electrophysiological techniques allow to
record from large population of neurons [\cite]. The recorded neurons
are usually picked out from a specific area according to an unknown process, and from their
observation in relation to stimuli or behavioral task, we strive for
understanding the mechanism behind neuronal coding. That is, they are assumed to be a
\enquote{representative random sample} of the neurons in that area.

@@

Using the pairwise \me\ models many studies investigated the
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? add more **
